Gaps in stellar streams as a result of globular cluster fly-bys

### 2024-12-12 paper/main.tex
Figure captions for gallery and decomposition

    \begin{figure*}
      \centering
      \includegraphics[width=\linewidth]{decomposition-monte-carlo-009-with-3-gaps.png}
      \caption{This figure decomposes the gaps shown in the middle panel of Fig.~\ref{fig:profiles} into the individual perturbers whose cause them, as identified from Fig.~\ref{fig:force-on-orbit}. These simulations only include the suspected globular clusters in one-at-a-time.}
      \label{fig:decomposition}
    \end{figure*}

@@

  \section{Gallery of Gaps} \label{sec:gallery_of_gaps}

    \begin{figure*}
      \centering
      \includegraphics[width=\linewidth]{gallery_of_gaps_monte-carlo-000.png}
      \includegraphics[width=\linewidth]{tau-profile-monte-carlo-000.png}
      \includegraphics[width=\linewidth]{gallery_of_gaps_monte-carlo-001.png}
      \includegraphics[width=\linewidth]{gallery_of_gaps_monte-carlo-002.png}
      \includegraphics[width=\linewidth]{tau-profile-monte-carlo-002.png}
      \caption{Gap Gallery}
      \label{fig:gallery0}
      \end{figure*}

    \begin{figure*}
      \centering
      \includegraphics[width=\linewidth]{gallery_of_gaps_monte-carlo-003.png}      
      \includegraphics[width=\linewidth]{gallery_of_gaps_monte-carlo-004.png}
      \includegraphics[width=\linewidth]{gallery_of_gaps_monte-carlo-005.png}
      \includegraphics[width=\linewidth]{gallery_of_gaps_monte-carlo-006.png}
      \includegraphics[width=\linewidth]{tau-profile-monte-carlo-006.png}
      \caption{Gap Gallery}
      \label{fig:gallery1}
      \end{figure*}

    \begin{figure*}
      \centering
      \includegraphics[width=\linewidth]{gallery_of_gaps_monte-carlo-007.png}
      \includegraphics[width=\linewidth]{gallery_of_gaps_monte-carlo-008.png}
      \includegraphics[width=\linewidth]{gallery_of_gaps_monte-carlo-009.png}      
      \includegraphics[width=\linewidth]{gallery_of_gaps_monte-carlo-010.png}
      \includegraphics[width=\linewidth]{gallery_of_gaps_monte-carlo-011.png}
      \caption{Gap Gallery}
      \label{fig:gallery2}
      \end{figure*}

    \begin{figure*}
      \centering
      \includegraphics[width=\linewidth]{gallery_of_gaps_monte-carlo-012.png}
      \includegraphics[width=\linewidth]{gallery_of_gaps_monte-carlo-013.png}
      \includegraphics[width=\linewidth]{gallery_of_gaps_monte-carlo-014.png}      
      \includegraphics[width=\linewidth]{gallery_of_gaps_monte-carlo-015.png}
      \includegraphics[width=\linewidth]{gallery_of_gaps_monte-carlo-016.png}
      \caption{Gap Gallery}
      \label{fig:gallery3}
      \end{figure*}

    \begin{figure*}
      \centering
      \includegraphics[width=\linewidth]{gallery_of_gaps_monte-carlo-017.png}
      \includegraphics[width=\linewidth]{gallery_of_gaps_monte-carlo-018.png}
      \includegraphics[width=\linewidth]{gallery_of_gaps_monte-carlo-019.png}      
      \includegraphics[width=\linewidth]{gallery_of_gaps_monte-carlo-020.png}
      \includegraphics[width=\linewidth]{gallery_of_gaps_monte-carlo-021.png}
      \caption{Gap Gallery}
      \label{fig:gallery4}
      \end{figure*}

    \begin{figure*}
      \centering
      \includegraphics[width=\linewidth]{gallery_of_gaps_monte-carlo-022.png}
      \includegraphics[width=\linewidth]{gallery_of_gaps_monte-carlo-023.png}
      \includegraphics[width=\linewidth]{gallery_of_gaps_monte-carlo-024.png}   
      \includegraphics[width=\linewidth]{tau-profile-monte-carlo-024.png}
      \includegraphics[width=\linewidth]{gallery_of_gaps_monte-carlo-025.png}
      \caption{Gap Gallery}
      \label{fig:gallery5}
      \end{figure*}

    \begin{figure*}
      \centering
      \includegraphics[width=\linewidth]{gallery_of_gaps_monte-carlo-026.png}
      \includegraphics[width=\linewidth]{gallery_of_gaps_monte-carlo-027.png}
      \includegraphics[width=\linewidth]{gallery_of_gaps_monte-carlo-028.png}
      \includegraphics[width=\linewidth]{tau-profile-monte-carlo-028.png}
      \caption{Gap Gallery}
      \label{fig:gallery6}
      \end{figure*}

    \begin{figure*}
      \centering      
      \includegraphics[width=\linewidth]{gallery_of_gaps_monte-carlo-029.png}    
      \includegraphics[width=\linewidth]{tau-profile-monte-carlo-029.png}  
      \includegraphics[width=\linewidth]{gallery_of_gaps_monte-carlo-030.png}
      \includegraphics[width=\linewidth]{tau-profile-monte-carlo-030.png}
      \includegraphics[width=\linewidth]{gallery_of_gaps_monte-carlo-031.png}
      \caption{Gap Gallery}
      \label{fig:gallery7}
      \end{figure*}

    \begin{figure*}
      \centering
      \includegraphics[width=\linewidth]{gallery_of_gaps_monte-carlo-032.png}
      \includegraphics[width=\linewidth]{gallery_of_gaps_monte-carlo-033.png}
      \includegraphics[width=\linewidth]{gallery_of_gaps_monte-carlo-034.png}      
      \includegraphics[width=\linewidth]{gallery_of_gaps_monte-carlo-035.png}
      \includegraphics[width=\linewidth]{gallery_of_gaps_monte-carlo-036.png}      
      \caption{Gap Gallery}
      \label{fig:gallery8}
      \end{figure*}

    \begin{figure*}
      \centering
      \includegraphics[width=\linewidth]{gallery_of_gaps_monte-carlo-037.png}
      \includegraphics[width=\linewidth]{gallery_of_gaps_monte-carlo-038.png}
      \includegraphics[width=\linewidth]{gallery_of_gaps_monte-carlo-039.png}
      \includegraphics[width=\linewidth]{gallery_of_gaps_monte-carlo-040.png}
      \includegraphics[width=\linewidth]{gallery_of_gaps_monte-carlo-041.png}      
      \caption{Gap Gallery}
      \label{fig:gallery9}
    \end{figure*}

    \begin{figure*}
      \centering
      \includegraphics[width=\linewidth]{gallery_of_gaps_monte-carlo-042.png}
      \includegraphics[width=\linewidth]{gallery_of_gaps_monte-carlo-043.png}
      \includegraphics[width=\linewidth]{gallery_of_gaps_monte-carlo-044.png}
      \includegraphics[width=\linewidth]{tau-profile-monte-carlo-044.png}
      \includegraphics[width=\linewidth]{gallery_of_gaps_monte-carlo-045.png}
      \caption{Gap Gallery}
      \label{fig:gallery010}
    \end{figure*}

    \begin{figure*}
      \centering
      \includegraphics[width=\linewidth]{gallery_of_gaps_monte-carlo-046.png}
      \includegraphics[width=\linewidth]{gallery_of_gaps_monte-carlo-047.png}
      \includegraphics[width=\linewidth]{gallery_of_gaps_monte-carlo-048.png}
      \includegraphics[width=\linewidth]{tau-profile-monte-carlo-048.png}
      \includegraphics[width=\linewidth]{gallery_of_gaps_monte-carlo-049.png}
      \caption{Gap Gallery}
      \label{fig:gallery11}
    \end{figure*}

>>>>

    \begin{figure*}
      \centering
      \includegraphics[width=\linewidth]{decomposition-monte-carlo-009-with-3-gaps.png}
      \caption{Density maps of Palomar~5's stream in the tail coordinate system. The colorscale represents normalized particle counts (total: 100,000). The top panel shows the \texttt{full} simulation with three gaps on the stream's right-hand side. The next three panels depict simulations with identical initial conditions but exclude the gravitational influence of all clusters except those forming a given gap. The \texttt{Reference} simulation omits other globular clusters. The bottom panel compares Palomar5's observed stream length to the \texttt{Reference} simulation, using the same Monte Carlo realization as Fig.\ref{fig:stream_on_sky} and \texttt{Sampling~009} of Fig.~\ref{fig:gallery2}.}
      \label{fig:decomposition}
    \end{figure*}

@@

  \section{Gallery of Gaps} \label{sec:gallery_of_gaps}
    Figures~\ref{fig:gallery0}-\ref{fig:gallery11} include all of the realizations of the \texttt{full} simulations of Palomar~5 in tail coordinates. If a gap is present, it is indicated by a red arrow with the responsible globular cluster. For the gaps that are not easily visible, we show the 1D profiles  showing the significant underdensities compared to the \texttt{reference} simulations. For instance, the second and last panels of Fig.~\ref{fig:gallery0}

    \begin{figure*}
      \centering
      \includegraphics[width=\linewidth]{gallery_of_gaps_monte-carlo-000.png}
      \includegraphics[width=\linewidth]{tau-profile-monte-carlo-000.png}
      \includegraphics[width=\linewidth]{gallery_of_gaps_monte-carlo-001.png}
      \includegraphics[width=\linewidth]{gallery_of_gaps_monte-carlo-002.png}
      \includegraphics[width=\linewidth]{tau-profile-monte-carlo-002.png}
      \caption{First gap gallery. See the text in Appendix~\ref{sec:gallery_of_gaps} for a description.}
      \label{fig:gallery0}
      \end{figure*}

    \begin{figure*}
      \centering
      \includegraphics[width=\linewidth]{gallery_of_gaps_monte-carlo-003.png}      
      \includegraphics[width=\linewidth]{gallery_of_gaps_monte-carlo-004.png}
      \includegraphics[width=\linewidth]{gallery_of_gaps_monte-carlo-005.png}
      \includegraphics[width=\linewidth]{gallery_of_gaps_monte-carlo-006.png}
      \includegraphics[width=\linewidth]{tau-profile-monte-carlo-006.png}
      \caption{Second gap gallery}
      \label{fig:gallery1}
      \end{figure*}

    \begin{figure*}
      \centering
      \includegraphics[width=\linewidth]{gallery_of_gaps_monte-carlo-007.png}
      \includegraphics[width=\linewidth]{gallery_of_gaps_monte-carlo-008.png}
      \includegraphics[width=\linewidth]{gallery_of_gaps_monte-carlo-009.png}      
      \includegraphics[width=\linewidth]{gallery_of_gaps_monte-carlo-010.png}
      \includegraphics[width=\linewidth]{gallery_of_gaps_monte-carlo-011.png}
      \caption{Third gap gallery}
      \label{fig:gallery2}
      \end{figure*}

    \begin{figure*}
      \centering
      \includegraphics[width=\linewidth]{gallery_of_gaps_monte-carlo-012.png}
      \includegraphics[width=\linewidth]{gallery_of_gaps_monte-carlo-013.png}
      \includegraphics[width=\linewidth]{gallery_of_gaps_monte-carlo-014.png}      
      \includegraphics[width=\linewidth]{gallery_of_gaps_monte-carlo-015.png}
      \includegraphics[width=\linewidth]{gallery_of_gaps_monte-carlo-016.png}
      \caption{Fourth gap gallery}
      \label{fig:gallery3}
      \end{figure*}

    \begin{figure*}
      \centering
      \includegraphics[width=\linewidth]{gallery_of_gaps_monte-carlo-017.png}
      \includegraphics[width=\linewidth]{gallery_of_gaps_monte-carlo-018.png}
      \includegraphics[width=\linewidth]{gallery_of_gaps_monte-carlo-019.png}      
      \includegraphics[width=\linewidth]{gallery_of_gaps_monte-carlo-020.png}
      \includegraphics[width=\linewidth]{gallery_of_gaps_monte-carlo-021.png}
      \caption{Fifth gap gallery}
      \label{fig:gallery4}
      \end{figure*}

    \begin{figure*}
      \centering
      \includegraphics[width=\linewidth]{gallery_of_gaps_monte-carlo-022.png}
      \includegraphics[width=\linewidth]{gallery_of_gaps_monte-carlo-023.png}
      \includegraphics[width=\linewidth]{gallery_of_gaps_monte-carlo-024.png}   
      \includegraphics[width=\linewidth]{tau-profile-monte-carlo-024.png}
      \includegraphics[width=\linewidth]{gallery_of_gaps_monte-carlo-025.png}
      \caption{Sixth gap gallery}
      \label{fig:gallery5}
      \end{figure*}

    \begin{figure*}
      \centering
      \includegraphics[width=\linewidth]{gallery_of_gaps_monte-carlo-026.png}
      \includegraphics[width=\linewidth]{gallery_of_gaps_monte-carlo-027.png}
      \includegraphics[width=\linewidth]{gallery_of_gaps_monte-carlo-028.png}
      \includegraphics[width=\linewidth]{tau-profile-monte-carlo-028.png}
      \caption{Seventh gap gallery}
      \label{fig:gallery6}
      \end{figure*}

    \begin{figure*}
      \centering      
      \includegraphics[width=\linewidth]{gallery_of_gaps_monte-carlo-029.png}    
      \includegraphics[width=\linewidth]{tau-profile-monte-carlo-029.png}  
      \includegraphics[width=\linewidth]{gallery_of_gaps_monte-carlo-030.png}
      \includegraphics[width=\linewidth]{tau-profile-monte-carlo-030.png}
      \includegraphics[width=\linewidth]{gallery_of_gaps_monte-carlo-031.png}
      \caption{Eigth gap gallery}
      \label{fig:gallery7}
      \end{figure*}

    \begin{figure*}
      \centering
      \includegraphics[width=\linewidth]{gallery_of_gaps_monte-carlo-032.png}
      \includegraphics[width=\linewidth]{gallery_of_gaps_monte-carlo-033.png}
      \includegraphics[width=\linewidth]{gallery_of_gaps_monte-carlo-034.png}      
      \includegraphics[width=\linewidth]{gallery_of_gaps_monte-carlo-035.png}
      \includegraphics[width=\linewidth]{gallery_of_gaps_monte-carlo-036.png}      
      \caption{Ninth gap gallery}
      \label{fig:gallery8}
      \end{figure*}

    \begin{figure*}
      \centering
      \includegraphics[width=\linewidth]{gallery_of_gaps_monte-carlo-037.png}
      \includegraphics[width=\linewidth]{gallery_of_gaps_monte-carlo-038.png}
      \includegraphics[width=\linewidth]{gallery_of_gaps_monte-carlo-039.png}
      \includegraphics[width=\linewidth]{gallery_of_gaps_monte-carlo-040.png}
      \includegraphics[width=\linewidth]{gallery_of_gaps_monte-carlo-041.png}      
      \caption{Tenth gap gallery.}
      \label{fig:gallery9}
    \end{figure*}

    \begin{figure*}
      \centering
      \includegraphics[width=\linewidth]{gallery_of_gaps_monte-carlo-042.png}
      \includegraphics[width=\linewidth]{gallery_of_gaps_monte-carlo-043.png}
      \includegraphics[width=\linewidth]{gallery_of_gaps_monte-carlo-044.png}
      \includegraphics[width=\linewidth]{tau-profile-monte-carlo-044.png}
      \includegraphics[width=\linewidth]{gallery_of_gaps_monte-carlo-045.png}
      \caption{Eleventh gap gallery}
      \label{fig:gallery010}
    \end{figure*}

    \begin{figure*}
      \centering
      \includegraphics[width=\linewidth]{gallery_of_gaps_monte-carlo-046.png}
      \includegraphics[width=\linewidth]{gallery_of_gaps_monte-carlo-047.png}
      \includegraphics[width=\linewidth]{gallery_of_gaps_monte-carlo-048.png}
      \includegraphics[width=\linewidth]{tau-profile-monte-carlo-048.png}
      \includegraphics[width=\linewidth]{gallery_of_gaps_monte-carlo-049.png}
      \caption{Twelfth gap gallery}
      \label{fig:gallery11}
    \end{figure*}
